LSOA domestic Electricty and Gas maps

### 2021-09-02 LSOA domestic Elec and Gas.Rmd

```{r addFacetsToElecDiff}
# or without colour but using facets for Local Authorities
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =100*(de_diff/de2010), 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "% change") +
  facet_wrap(`Local Authority Name.x` ~ .)

>>>>

Try adding facets for each Local Authority
```{r addFacetsToElecDiff}
# or without colour but using facets for Local Authorities
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =100*(de_diff/de2010), 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "% change") +
  facet_wrap(`Local Authority Name.x` ~ .)
